Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2019-12-16 rainbowCAM.tex

The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes. In summary, we have shown that, for the intermediate and high angles, these scattering amplitudes can be reconstructed in terms of Regge poles with great precision in the regime of intermediate and high frequencies. It is important to note that for compact objects (\textit{i.e.}, $R/M=6$), we observed that it is necessary to take into account the background integral contributions to describe the glory and this regardless of the frequency. Which does not the case for UCOs since only the sum over the Regge poles is enough. Moreover, the sum over the Regge poles permitted us to overcome the difficulties linked to the lack of convergence from which the scattering amplitude suffers (\textit{i.e.} partial wave expansions) due to the long-range of the field propagating on the Schwarzschild black hole (outside the compact body). However, the existence of the broad resonance branch (see also narrow resonance branch for the UCOs) close to the real axis with an approximately uniform spacing, $\Delta\lambda\sim 2 $, requires the calculation of a large number of poles. In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes  (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a few poles ($<5$) capture both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}. Also, in the case of the Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles using the Debye expansion (see the chapter 9 of the monograph of Nussenzveig \cite{Nussenzveig:2006}), thereby eliminating the broad resonance branch entirely and accelerating the convergence. This is a possible direction for a future investigation

>>>>

The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes. In summary, we have shown that, for the intermediate and high angles, these scattering amplitudes can be reconstructed in terms of Regge poles with great precision in the intermediate and high frequencies regime. It is important to note that for compact objects (\textit{i.e.}, $R/M=6$), we observed that it is necessary to take into account the background integral contributions to describe the glory and this regardless of the frequency. Which does not the case for UCOs since only the sum over the Regge poles is enough. Moreover, the sum over the Regge poles permitted us to overcome the difficulties linked to the lack of convergence from which the scattering amplitude suffers (\textit{i.e.} partial wave expansions) due to the long-range of the field propagating on the Schwarzschild black hole (outside the compact body). However, the existence of the broad resonance branch (see also narrow resonance branch for the UCOs) close to the real axis with an approximately uniform spacing, $\Delta\lambda\sim 2$, requires the calculation of a large number of poles. In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a few poles ($<5$) capture both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}. Also, in the case of the Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles using the Debye expansion (see the chapter 9 of the monograph of Nussenzveig \cite{Nussenzveig:2006}), thereby eliminating the broad resonance branch entirely and accelerating the convergence. This is a possible direction for a future investigation
